Self Regulation Ontology Retest Analyses

### 2018-03-21 code/SRO_Retest_Analyses.Rmd
refactoring

```{r}
rel_comp = rel_comp %>%
  mutate(diff_sq = abs(mean_icc - retest_reliability)^2)

rel_comp %>%
  ggplot(aes(sample_size,diff_sq, color=task))+
  # geom_point()+
  #exponential decay (linearized by taking logs of both sides)
  geom_smooth(method="glm",se=FALSE, method.args=list(family=gaussian(link="log")))+
  theme_bw()
```

@@

```{r}
with(rel_comp %>% filter(task == "task"), cor(mean_icc, mean_reliability))
```

```{r}
with(rel_comp %>% filter(task == "survey"), cor(mean_icc, mean_reliability))
```

@@

```{r}
mod4 = lmer(retest_reliability ~ mean_icc + scale(days) + scale(sample_size) + (mean_icc|dv), data=rel_comp)

@@

Same result if you do flat model without random slopes for dv's

```{r}
summary(lm(retest_reliability ~ mean_icc+scale(sample_size), data=rel_comp))
```

Visualize hierarchical model:
How would I show random intercepts/slopes? Does the fact that I can't think of how means that there is something wrong with the model?

```{r}
rel_comp %>%
  ggplot()+  
  geom_boxplot(aes(mean_icc, retest_reliability, group=dv))+
  geom_smooth(aes(mean_icc, retest_reliability), method= 'lm')+
  theme_bw()+
  theme(legend.position = 'none')+
  geom_abline(slope=1, intercept=0)+
  # geom_abline(slope=0, intercept=0.3, linetype='dashed')+
  xlim(-0.2, 1)+
  ylim(-0.2, 1)+
  facet_grid(task~.)+
  xlab('Mean bootstrapped ICC')+
  ylab('Reliability estimate from literature')

@@

Potential problems in this graph: 
- not all metrics are ICC's
- difference in delay between completion of two tests (does it make a difference in the lit review?)

>>>>

```{r}
rel_comp = rel_comp %>%
  mutate(diff_sq = (mean_icc - retest_reliability)^2)

rel_comp %>%
  ggplot(aes(sample_size,diff_sq, color=task))+
  # geom_point()+
  #exponential decay (linearized by taking logs of both sides)
  geom_smooth(method="glm",se=FALSE, method.args=list(family=gaussian(link="log")))+
  theme_bw()+
  theme(legend.title = element_blank())
```

@@

```{r}
with(rel_comp %>% filter(task == "task"), cor(mean_icc, retest_reliability))
```

```{r}
with(rel_comp %>% filter(task == "survey"), cor(mean_icc, retest_reliability))
```

@@

```{r}
mod4 = lmer(retest_reliability ~ mean_icc + task + scale(sample_size) + (mean_icc|dv), data=rel_comp)

@@

Visualize hierarchical model:
How would I show random intercepts/slopes?

```{r}
rel_comp %>%
  ggplot()+  
  geom_boxplot(aes(mean_icc, retest_reliability, group=dv))+
  geom_smooth(aes(mean_icc, retest_reliability), method= 'lm')+
  theme_bw()+
  theme(legend.position = 'none')+
  geom_abline(slope=1, intercept=0)+
  geom_abline(slope=0, intercept=0.3, linetype='dashed')+
  xlim(-0.2, 1)+
  ylim(-0.2, 1)+
  # facet_grid(task~.)+
  xlab('Mean bootstrapped ICC')+
  ylab('Reliability estimate from literature')

@@

NOTE: not all metrics are ICC's
